---
title: "Preliminary Drosophila Larvae Crawling Assay On W- Genotype Control Groups In Response To Acute Temperature Shifts"
author: "Toby Shaw-McGrath"
output:
  bookdown::html_document2: default
  bookdown::word_document2: default
  bookdown::pdf_document: default
bibliography: ["references.bib", "packages.bib"]

---

```{r setup, include=FALSE}
# Setting defaults for the code chunks to come
knitr::opts_chunk$set(echo = FALSE,
                      warning = FALSE,
                      message = FALSE,
                      fig.retina = 3)
```

```{r packages}
source("R/00-pkg.R")

```

# Methods
### Data Gathering {-#methods}

###  Data Files {-#methods}


### Data Processing {-#methods}

```{r functions}
# Reads and cleans data into a neat data frame perfect for this specific analysis
# Ensures independence of observations by compressing all from one individual into one value
# Could be a method for the TemperatureCombo Class which would be called in the constructor instead of having the data frame as a parameter
source("R/functions/Bespoke_xlsx_reader.R")
```
```{r classes}
# Class that makes data analysis and storage easier (in my opinion) 
source("R/classes/TemperatureCombo_Class.R")
```
```{r import}
# Compile and process data
source("R/01-import.R") 
# Don't need to extract values for inline as the TemperatureCombo objects have summary data as attributes
```


# Results 
```{r analysis, include=FALSE}
# Run stat tests comparing the effects of measuring at an increased, lowered, or same temperature and then comparing the effect of reared temperature
# Results saved as lists that can be called in line for value
source("R/02-analysis.R")
```
## Tests Used {-#results}
  Welch two sample T tests and Wilcoxon signed rank tests were carried out via base R [@R-base] operations as part of a method in TemperatureCombo class. The shapiro_then_stats() method applied a Shapiro-Wilk test for normality then selected either a parametric or non-parametric depending on normality. 

  All 3 variables were compared in the following comparison groups:
  
* A: RT&deg;C at RT&deg;C x 29&deg;C at 29&deg;C
* B: RT&deg;C at RT&deg;C x RT&deg;C at 29&deg;C
* C: 29&deg;C at 29&deg;C x 29&deg;C at RT&deg;C


## Test Results
```{r plots,include=FALSE}
# Load the values for referencing later
source("R/03-plots.R")


```
  The results are broadly in-line with our hypothesis, only two tests came back with significant differences, both for distance. There was a significant difference for distance in groups A and C. Distance was the only variable with normal distribution in all groups, therefore, the Welch two sample T test was only used for distance and the Wilcoxon signed rank for the other variables.

### Group A

   
  <!-- Could really make a function to automate legends like with ggplot titles and labs -->
  

```{r fig-RTRT-2929W, fig.cap='(ref:fig-RTRT-2929W)'}
#grid.draw() outputs the grid as a Figure instead of a matrix
grid.draw(fig_RTRT_2929W)
```

```{r fig-RTRT-2929PGRPLE, fig.cap='(ref:fig-RTRT-2929PGRPLE)'}
grid.draw(fig_RTRT_2929PGRPLE)
```


### Group B

 

```{r fig-RTRT-RT29W, fig.cap='(ref:fig-RTRT-RT29W)'}
grid.draw(fig_RTRT_RT29W)
```
```{r fig-RTRT-RT29PGRPLE, fig.cap='(ref:fig-RTRT-RT29PGRPLE)'}
grid.draw(fig_RTRT_RT29PGRPLE)
```
### Group C
 
```{r fig-2929-29RTW, fig.cap='(ref:fig-2929-29RTW)'}
grid.draw(fig_2929_29RTW)
```

```{r fig-2929-29RTPGRPLE, fig.cap='(ref:fig-2929-29RTPGRPLE)'}
grid.draw(fig_2929_29RTPGRPLE)
```

```{r fig-RTRT-cross}
grid.draw(all_RTRT_cross)
```
```{r fig-RT29-cross}
grid.draw(all_RT29_cross)
```
```{r fig-2929-cross}
grid.draw(all_2929_cross)
```
```{r fig-29RT-cross}
grid.draw(all_29RT_cross)
```




## Word count {.unnumbered #word-count}

Word count calculated with **`wordcountaddin`**

```{r wordcount}
source("R/functions/wordcount.R")

main_rmd_words <- count_words("main.Rmd") %>%
  str_extract("[0-9]+") %>% 
  as.numeric()

# "Word count calculated with **`wordcountaddin`**" isn't really part of the report, plus I was very tight on words
main_rmd_words <- main_rmd_words - 5 

read_me_words <- count_words("README.md") %>%
  str_extract("[0-9]+") %>% 
  as.numeric()

```

This document: `r main_rmd_words`\
README: `r read_me_words`\
**Total: `r main_rmd_words + read_me_words`**


# References {-#References}

